Big Brother Is Watching

### 2015-11-05 manuscript.tex
Just a tweak to my part

\subsection{Performance}
\label{sub:greey_performance}
This strategy can tackle both density requirements. Figure~\ref{fig:greedy_performance} show the performance of this strategy when the jaywalker density is uniform and when it is not, respectively. The vertical axis represents the mean number of nodes left unwatched for too long per moment in time over 10 simulations, and the horizontal axis represents the number of drones in flight during the simulations. There is a slight difference between Figure~\ref{fig:random_uniform} and Figure~\ref{fig:random_nonuniform} in that when the jaywalker density isn't uniform, more drones are required. This is most likely due to the fact that Gotham University and the Financial District need to be watched so often that any strategy would require more drones. This strategy manages to appropriately cover 90\% of Manhattan with 70 drones and 75 drones when the jaywalker density is uniform and nonuniform respectively, and 97.5\% of Manhattan with 90 and 95 drones respectively. One could keep adding arbitrarily many drones, but with diminishing results.

>>>>

\subsection{Performance}
\label{sub:greey_performance}
This strategy can tackle both density requirements. Figure~\ref{fig:greedy_performance} show the performance of this strategy when the jaywalker density is uniform and when it is not, respectively. The vertical axis represents the mean number of nodes left unwatched for too long per moment in time over 10 simulations, and the horizontal axis represents the number of drones in flight during the simulations. There is a slight difference between Figure~\ref{fig:random_uniform} and Figure~\ref{fig:random_nonuniform} in that when the jaywalker density isn't uniform, more drones are required. This is most likely due to the fact that Gotham University and the Financial District need to be watched so often that any strategy would require more drones. This strategy manages to appropriately cover 90\% of Manhattan with 70 drones and 75 drones when the jaywalker density is uniform and nonuniform respectively, and 97.5\% of Manhattan with 90 and more than 100 drones respectively. One could keep adding arbitrarily many drones, but with diminishing results.
